SVG: The Paper

### 2022-04-20 Analysis/index.Rmd
some small edits

# compute the average weight for each participant x condition x item selection
# also compute the proportion of times in which the item selected by the 
# participant was judged the most likely to be selected by our model.

a %>% group_by(condition, observer, found) %>%
  summarise(meanb = mean(b),
            prop_best = mean(selected_max), .groups = "drop") %>%
  # finally, also compute what we would expect under a null-model
  mutate(chance = 1/(41-found))-> a_agg
```

@@

```{r, echo = TRUE}
my_breaks = seq(0.0, 1, 0.05)

@@

We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight).

We can also repeat this calculation for the 2nd and 3rd ranked candidate items.

@@

plt1 + plt2

```

```{r}
rm(a_cut)
```

Here we can see that these candidate items are typically underweight.

@@

```{r, echo = TRUE}
summary(lm(accuracy ~ condition * bP, 
           data = filter(fit, is_outlier == 0)))

summary(lm(accuracy ~ bP + pS + bM + bP, 
           data = filter(fit, is_outlier == 0)))

```

@@

trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)

# 
source("functions/plot_trial.R")
```

@@

```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
plts <- map(1:3, plot_trial, trls_easy, a, d)

@@

@@

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom')

```

```{r}

```

@@

```{r}
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()
```

```{r fig.cap="Distirbution of median intial selection."}

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()

```

@@

```

>>>>

# compute the average weight for each participant x condition x item selection
# also compute the proportion of times in which the item selected by the 
# participant was judged the most likely to be selected by our model.
a %>% group_by(condition, observer, found) %>%
  summarise(meanb = mean(b),
            prop_best = mean(selected_max), .groups = "drop") %>%
  # finally, also compute what we would expect under a null-model
  mutate(chance = 1/(41-found))-> a_agg
```

@@

```{r, echo = TRUE}
my_breaks <- seq(0.0, 1, 0.05)

@@

We can see from the Figure below that our model is well-calibrated (at least in terms of the target with the highest assigned weight). If we repeat this calculation for the 2nd and 3rd ranked candidate items we can see that we slightly underweight these items, but we are still pretty accurate.

@@

plt1 + plt2
```

```{r}
rm(a_cut, my_breaks, plt1, plt2)
```

@@

```{r, echo = TRUE}
dm <- filter(fit, is_outlier == 0)

summary(lm(accuracy ~ condition * bP, 
           data = dm))

summary(lm(accuracy ~ bP + pS + bM + bP, 
           data = dm))

rm(dm)
```

@@

trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
trls_mid  <- filter(a_trl, prop_max > qs[2], prop_max < qs[3]) %>% sample_n(3)
trls_easy <- filter(a_trl, prop_max > qs[4]) %>% sample_n(3)
```

@@

```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}

source("functions/plot_trial.R")
plts <- map(1:3, plot_trial, trls_easy, a, d)

@@

```{r}
rm(trls_easy, trls_mid, trls_hard, plts, qs)
```

@@

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom')
```

```{r}
rm(path_lengths, plt1, plt2)
```

@@

```{r echo = TRUE}
# Reimport data again (as we removed the inital target selection earlier)
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))
```

```{r fig.height = 3.5, fig.cap="(*left*) Density plot for initial target selections, over all participants and all trials. (*right*) Median $x$ and $y$ coordinates for the initial target selection for each participant."}
my_theme <- theme(axis.line=element_blank(),axis.text.x=element_blank(),
          axis.text.y=element_blank(),axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),legend.position="none",
          panel.background=element_rect(color  = "#808080", size = 2,linetype = 'dotted', fill ="#808080"),
        panel.border= element_rect(colour = "black", fill=NA, size=5),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank())

ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
  scale_fill_viridis_c() + scale_color_viridis_c() +
  my_theme -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()+ scale_color_viridis_c() +
  my_theme -> plt_med

plt_all + plt_med

rm(plt_all, plt_med)
```

We can model this as a mixture of Gaussians.

@@

ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
  scale_fill_viridis_c() + scale_color_viridis_c() +
  my_theme -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()+ scale_color_viridis_c() +
  my_theme -> plt_med

plt_all + plt_med 
```
